Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-20 manu-draft.Rmd
transect example picture dates descending, x axis labels changed

```{r trnex, fig.cap = 'Results for (a) seagrass and (b) macroalgae rapid response transect surveys at a site (S3T6, -82.55866 W longitude, 27.64483 N latitude) near Piney Point.  Sample dates in 2021 are shown in rows with transect meter results shown in columns. Results show dominance of manatee grass (*Syringodium filiforme*) and red macroalgae groups, with abundances of *Dapis sp.* (cyanobacteria) peaking in June and green macroalgae (*Ulva spp.*) increasing in July.  Abundances are Braun-Blanquet coverage estimates.'}
knitr::include_graphics(here('figs/trnex.jpeg'))
```

>>>>

```{r trnex, fig.cap = 'Results for (a) macroalgae and (b) seagrass rapid response transect surveys at a site (S3T6, -82.55866 W longitude, 27.64483 N latitude) near Piney Point.  Sample dates in 2021 are shown in rows with transect meter results shown in columns. Results show dominance of manatee grass (*Syringodium filiforme*) and red macroalgae groups, with abundances of *Dapis sp.* (cyanobacteria) peaking in June and green macroalgae (*Ulva spp.*) increasing in July.  Abundances are Braun-Blanquet coverage estimates.'}
knitr::include_graphics(here('figs/trnex.jpeg'))
```
